A Fredholm integral equation approach to computing Stokes eigenvalues in the plane

### 2019-03-12 doc/draft-01-stokes/03analysis2.tex
Updating fredholm determinant section

As noted in~\cite{zhao2015robust}, this lack of one-to-one correspondance between
the invertibility of the integral operator $\cI - 2\cD_{k} - 2\cW$
and the Dirichlet eigenvalues of the Stokes operator on multiply
connected domains causes non-robustness and introduces near 
resonanaces for simply connected domains
which are almost multiply connected. 
This issues is discussed in detail
in example~\cref{sec:numanalysis-nearly-mult-con}.

@@

The following lemma shows that the operator 
$-2\cD_{k} - 2\cW$ is a trace class operator.
\begin{lemma} 
$-2\cD_{k} - 2\cW$ is a trace class operator for all $k$ 
\end{lemma}
\begom{proof}
Using Bessel function asymptotics, we note that the
kernel of $\cD_{k}$ given by
$\TT_{\cdot,\cdot,\ell}\nu_{\ell}(\bx,\by)$
has a leading order singularity of $|\bx-\by|^2 \log{|\bx-\by|^2}$ as $\bx\to \by$.
It follows from~\cite{bornemann2010} numerical that $\cD_{k}$
is a trace-class operator for all $k$.
Since $\cW$ is a rank-one perturbation independent of $k$, and trace-class
operators are a vector space, we conclude that
$-2\cD_{k} - 2\cW$ is also a trace-class operator for all $k$.
\end{proof}

@@

We now show how this fact can be used numerically
to estimate the Dirichlet eigenvalues.
Suppose that $M_{k}^{N}$ is a Nystr\"{o}m discretization 
of the operator $-2\cD_{k} - 2\cW$ when the boundary 
$\Gamma$ is discretized with $N$ points. 
Let $f^{N}(k) = \text{det}(I + M_{k}^{N})$
where here $\text{det}$ is the standard matrix determinant.
Note that the discretized matrix also depends on the choice
of quadrature rule used in the Nystr\"{o}m discretization
of the operator.
In~\cite{zhao2015robust}, the authors prove that
for computing the Laplace eigenvalues on regions with 
analytic boundaries, when the integral
operators are discretized using Kress-quadratures,
the determinant of the Nystr\"{o}m discretized operators
at the true eigenvalues converge to $0$ exponentially in $N$.
This combined with the analyticity of $f^{N}(k)$ as a function
of $k$ for fixed $N$ proves that

>>>>

As noted in~\cite{zhao2015robust}, this lack of one-to-one correspondance between
the invertibility of the integral operator $\cI - 2\cD_{k} - 2\cW$
and the Dirichlet eigenvalues of the Stokes operator on multiply
connected domains causes non-robustness and introduces near 
resonanaces for simply connected domains
which are almost multiply connected. 
This issue is discussed in detail
in example~\cref{sec:numanalysis-nearly-mult-con}.

@@

The following lemma shows that the operator 
$-2\cD_{k} - 2\cW$ is a trace class operator.
\begin{lemma} 
$-2\cD_{k} - 2\cW$ is a trace class operator for all $k$ 
\end{lemma}
\begin{proof}
Using Bessel function asymptotics, we note that the
kernel of $\cD_{k}$ given by
$\TT_{\cdot,\cdot,\ell}\nu_{\ell}(\bx,\by)$
has a leading order singularity of $|\bx-\by|^2 \log{|\bx-\by|^2}$ as $\bx\to \by$.
It follows from~\cite{bornemann2010} numerical that $\cD_{k}$
is a trace-class operator for all $k$.
Since $\cW$ is a rank-one perturbation independent of $k$, and trace-class
operators are a vector space, we conclude that
$-2\cD_{k} - 2\cW$ is also a trace-class operator for all $k$.
\end{proof}

@@

We now show how this fact can be used numerically
to estimate the Dirichlet eigenvalues.
Suppose that $M_{k}^{N}$ is a Nystr\"{o}m discretization 
of the operator $-2\cD_{k} - 2\cW$ when the boundary 
$\Gamma$ is discretized with $N$ points. 
Let $f^{N}(k) = \text{det}(I + M_{k}^{N})$
where here $\text{det}$ is the standard matrix determinant.
Note that the discretized matrix also depends on the choice
of quadrature rule used in the Nystr\"{o}m discretization
of the operator.

In~\cite{zhao2015robust}, the authors prove that
for computing the Laplace eigenvalues on regions with 
analytic boundaries, when the integral
operators are discretized using Kress-quadratures,
the determinant of the Nystr\"{o}m discretized operators
at the true eigenvalues converge to $0$ exponentially in $N$.
Thus, is the eigenvalues have multiplicity $1$, i.e. the
derivative of the determinant is non-zero at the true-eigenvalues,
then the analyticity of the discretized determinant implies
that the zeros of the determinant of the Nystr\"{o}m 
discretization of the linear operator converges
exponentially to the true Dirichlet eigenvalues for Laplace's equation.

The proof presented in~\cite{zhao2015robust} carries forward
for computing the Dirichlet eigenvalues of Stokes equation as well.
We summarize the result in the following theorem.
\begin{thrm}
Suppose that $\Omega$ is a simply connected domain with an analytic boundary.
Let $k_{j}$, $j=1,2,\ldots M$ denote all the Dirichlet eigenvalues of Stokes
equation on $\Omega$ contained in the interval $[a,b]$. 
Suppose further that all the eigenvalues have multiplicity $1$.
Let $f^{N}(k) = \text{det}(I+M^{N}_{k})$, where $M^{N}_{k}$ 
is the Nystr\"{o}m discretzation of $-2\cD_{k} - 2\cW$ with Kress
quadratures.
Then $f^{N}(k)$ has exactly $M$ zeros on the interval $[a,b]$. 
Let $\omega_{j}$, $j=1,2\ldots M$ denote the zeros of $f^{N}$.
Furthermore, there exist constants $a>0$ and $C$, 
such that $\sup_{j=1}^{M} |\omega_{j} - k_{j}| < C e^{-aN}$.
\end{thrm}

\begin{proof}
The proof follows from small modificiations of the proofs contained in~\cite{zhao2015robust}. 
\end{proof}
